### 2023-10-10 mycv/subs/papers.tex
updates in papers

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, M.-S. Kim, S. Choi, \underline{Y. Jeong}$^*$}
  {\href{}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
  {Journal of Magnesium and Alloys}
  {Accepted}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {M. Joo, M.-S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C N. Tom\'{e}, B. Jeon, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback   }}
  {In press}
  {}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {J. Park, \underline{Y. Jeong}$^*$}
  {\href{http://dx.doi.org/10.3365/KJMM.2022.60.8.607}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}}
  {Korean Journal of Metals and Materials}
  {Vol. 60 (8), 607-618, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {M.S. Lee, T. Kawasaki, T. Yamashita, S. Harjo, Y.T. Hyun, \underline{Y. Jeong}, T. S. Jun$^*$}
  {\href{https://doi.org/10.1038/s41598-022-07640-3}{In-situ neutron diffraction study of lattice deformation behaviour of commercially pure titanium at cryogenic temperature}}
  {Scientific Reports}
  {Vol. 12 (1), 1-10, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, B. Jeon, C N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2021.103110}{Finite element analysis using an incremental elasto-visco-plastic self-consistent polycrystal model: FE simulations on Zr and low-carbon steel subjected to bending, stress-relaxation, and unloading}}
  {International Journal of Plasticity}
  {Vol. 147, 103110, 2021}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
  {International Journal of Plasticity}
  {Vol. 135, 102812, 2020}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D. Steglich}
  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
  {International Journal of Mechanical Sciences}
  {Vol. 181, 105680, 2020}
  {
  }

@@

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
\item
    \cventry
  {\underline{Y. Jeong}$^*$, Timo Manninen}
  {\href{http://iopscience.iop.org/article/10.1088/1742-6596/1063/1/012020}{Formability predictions and measurement of 316L stainless steel using self-consistent crystal plasticity}}
  {Journal of Physics: Conference Series}
  {Vol. 150673, 2018}
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {Thermal ratcheting of uranium simulated by a thermo-elasto-visco-plastic self-consistent polycrystal model}
  {submitted}
  {}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, S.-Y. Lee, J. Lee, \underline{Y. Jeong}$^*$}
  {Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}
  {in preparation}
  {}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, M.-S. Lee, T.-S. Jun, \underline{Y. Jeong}$^*$}
  {Temperature-dependent behavior of CP-Ti interpreted via self-consistent crystal plasticity simulation}
  {submitted}
  {}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, M.-S. Kim, S. Choi, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.jma.2022.10.017}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
  {Journal of Magnesium and Alloys}
  {Vol. 11(4), p1393-1407, 2023}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {M. Joo, M.-S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C N. Tom\'{e}, B. Jeon, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback}}
  {International Journal of Mechanical Sciences}
  {Vol. 237, 107796, 2023}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {Lalit Kauschik, Ki-Seong Park, Jeong-Gyun Kim, Jae-Seong Lee, \underline{Youngung Jeong}, Shi-Hoon Choi$^*$}
  {\href{https://doi.org/10.1016/j.ijplas.2022.103467}{Reconstructing orientation data from the images of IPF maps and ODF sections extracted from the literature: A data-collection method for machine learning}}
  {International Journal of Plasticity}
  {Vol. 159, 103467, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {J. Park, \underline{Y. Jeong}$^*$}
  {\href{http://dx.doi.org/10.3365/KJMM.2022.60.8.607}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}}
  {Korean Journal of Metals and Materials}
  {Vol. 60 (8), 607-618, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {M.S. Lee, T. Kawasaki, T. Yamashita, S. Harjo, Y.T. Hyun, \underline{Y. Jeong}, T. S. Jun$^*$}
  {\href{https://doi.org/10.1038/s41598-022-07640-3}{In-situ neutron diffraction study of lattice deformation behaviour of commercially pure titanium at cryogenic temperature}}
  {Scientific Reports}
  {Vol. 12 (1), 1-10, 2022}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, B. Jeon, C N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2021.103110}{Finite element analysis using an incremental elasto-visco-plastic self-consistent polycrystal model: FE simulations on Zr and low-carbon steel subjected to bending, stress-relaxation, and unloading}}
  {International Journal of Plasticity}
  {Vol. 147, 103110, 2021}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
  {International Journal of Plasticity}
  {Vol. 135, 102812, 2020}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D. Steglich}
  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
  {International Journal of Mechanical Sciences}
  {Vol. 181, 105680, 2020}
  {
  }

@@

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\item
  % ---------------------------------------------------------
  \cventry
  {Carlos N. Tome$^*$, \underline{Y. Jeong}}
  {\href{https://doi.org/10.1007/978-3-031-40920-2_68}{Thermal Ratcheting of Uranium Simulated with a Thermo-Elasto-Visco-Plastic Polycrystal Model}}
  {Proceedings of the 14th International Conference on the Technology of Plasticity - Current Trends in the Technology of Plasticity}
  {}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {B. Jeon, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1007/978-3-031-40920-2_69}{Interpretation of the Unloading Non-linearity in Dual-Phase 980 Steel Using an Elasto-Visco-Plastic Self-consistent Polycrystal Model}}
  {Proceedings of the 14th International Conference on the Technology of Plasticity - Current Trends in the Technology of Plasticity}
  {}
  {
  }

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, Timo Manninen}
  {\href{http://iopscience.iop.org/article/10.1088/1742-6596/1063/1/012020}{Formability predictions and measurement of 316L stainless steel using self-consistent crystal plasticity}}
  {Journal of Physics: Conference Series}
  {Vol. 150673, 2018}
  {
  }
